%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-Stack Web Development} % Project title
    {Personal Project} % Project type/context
    {Apr 2023 - Present} % Date(s)
    {} % Location (empty if not needed)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a proof of concept web application showcasing web development skills using Flask/Jinja2, HTML, CSS, and JavaScript.}
        \item {Implemented front-end components and back-end functionality, including user authentication, MongoDB operations, Docker containerization, password encryption, and AWS Beanstalk deployment.}
        \item {Employed optimization techniques for faster loading speed and applied industry best practices for version control, code documentation, and coding standards.}
        \item {Skills used: Cloud Development, Agile Development, Git, MongoDB, Flask, Node.js, React.js, HTML, CSS, JavaScript.}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Kaggle Competition} % Project title
    {Data Science/ML Project} % Project type/context
    {} % Date(s)
    {} % Location (empty if not needed)
    {
      \begin{cvitems} % Description(s) of project
        \item {Utilized advanced Decision Forest techniques and TensorFlow for Linear Regression Models in a Kaggle competition focusing on housing price predictions.}
        \item {Leveraged statsmodels API to develop robust Ordinary Least Squares (OLS) models, optimizing for accuracy.}
        \item {Demonstrated expertise in machine learning techniques for predictive modeling.}
        \item {Skills used: Agile Development, Git, TensorFlow, statsmodels, Machine Learning.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
